Consistent Polyhedral Surrogates via Embedding

### 2019-05-17 notes/jessie-proof-sketches.tex
Clarified a few things

  Generating $\R := \{u_f\}_{f\in F}$, we know that $\gamma = \phi(\Gamma \cap \R)$, where the two are the same up to relabeling \jessie{need more thorough argument on this?} and $\Gamma \cap \R$ is elicited by $L|_\R$ by \jessie{COLT Lemma 11}, and thus has the same Bayes Risk as $L|_\R$ by \jessie{cite FK General Truthfulness Theorem 2}.
  Applying \jessie{COLT Lemma 11}, we then observe that $\risk{L} = \risk{L|_\R} = \risk{\ell}$.

@@

  First, assume that $\risk{\ell} \neq \risk{L} +c$ for any constant $c$.
  Denote by $P_\ell$ the facets of $\risk{\ell}$ projected onto $\simplex$, which must be different than the facets of $\risk{L}$ projected onto $\simplex$, denoted $P_L$.
  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}(p)$.
  Therefore, we know the argmins of $L$ and $\ell$ are unique and as the subgradients of the risks are not equal, then $r \in \argmin_{r'} \ell(r,p) \implies \varphi(r) \not \in \argmin_u L(u,p)$, and thus we contradict our embedding assumption.

>>>>

  Generating $\R := \{u_f\}_{f\in F}$, we know that $\gamma = \phi(\Gamma \cap \R)$, where the two are the same up to relabeling \jessie{need more thorough argument on this?  Not sure if I believe it...} and $\Gamma \cap \R$ is elicited by $L|_\R$ by \jessie{COLT Lemma 11}, and thus has the same Bayes Risk as $L|_\R$ by \jessie{cite FK General Truthfulness Theorem 2}.
  Applying \jessie{COLT Lemma 11}, we then observe that $\risk{L} = \risk{L|_\R} = \risk{\ell}$.

@@

  \jessie{TODO: If we use this, change notation of $P_\ell$ to match what's already in the paper}
  First, assume that $\risk{\ell} \neq \risk{L} +c$ for any constant $c$.
  Denote by $P_\ell$ the facets of $\risk{\ell}$ projected onto $\simplex$, which must be different than the facets of $\risk{L}$ projected onto $\simplex$, denoted $P_L$.
  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}(p)$.
  Therefore, we know the argmins of $L$ and $\ell$ are unique and as the subgradients of the risks are not equal, then $r \in \argmin_{r'} \ell(r,p) \implies \varphi(r) \not \in \argmin_u L(u,p)$, and thus we contradict our embedding assumption.
